Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
move Kmeans++
explain that 372 ms is a power of 2

Starting from a monophonic waveform $\boldsymbol{x}(t)$, the scattering transform is defined as an infinite cascade of wavelet transform and modulus operators.
However, to achieve invariance to translation up to $T = 372\,\mathrm{ms}$, \ie the approximately minimal duration between non-overlapping acoustic events, two layers of scattering transform.

@@

For ASC, the systems are again evaluated on the private part of DCASE2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public part of the DCASE2013 dataset, also using five-fold stratified cross validation. Clustering is done using KMeans$++$ \cite{arthur2007k}, an augmented version of K-means with a robust initialization procedure.

@@

\section{Results \label{sec:results}}

>>>>

Starting from a monophonic waveform $\boldsymbol{x}(t)$, the scattering transform is defined as an infinite cascade of wavelet transform and modulus operators.
However, to achieve invariance to translation up to $T = 372\,\mathrm{ms}$, \ie the approximately minimal duration between non-overlapping acoustic events, corresponding to $2^14 = 16384$ discrete-time samples at $44100\,\mathrm{Hz}$, two layers of scattering transform.

@@

For ASC, the systems are again evaluated on the private part of DCASE2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public part of the DCASE2013 dataset, also using five-fold stratified cross validation.

@@

Clustering is done using KMeans$++$ \cite{arthur2007k}, an augmented version of K-means with a robust initialization procedure.
\section{Results \label{sec:results}}
